### 2013-01-08 edupar-13/410.tex
polish some text

The work described takes place in the context of a
Computer Science class called
15-410, Operating System Design and Implementation.
It is designed for juniors and seniors in Computer Science
and Electrical and Computer Engineering.
For CS students it is one of five courses which fulfill
the ``Software Systems'' requirement (at present, the others
are Compiler Design,
Parallel Computer Architecture and Programming,
Distributed Systems,
and Computer Networks.
The prerequisite course is 15-213,
Introduction to Computer Systems,
a course which has been adopted at other
universities in the U.S.\ and worldwide~\cite{sigcse01:CSaPP}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% XXX How do we say politely "Some M.S. students
% manage to pass it too"?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section we will discuss the course learning
objectives,
outline the programming projects,
discuss our use of Wind River Simics as the
the basic simulation/debugging environment,
and close by mentioning current limitations in the scope
of the course material.

@@

\subsubsection{Automated tests}
We run submitted kernels in an automated testing harness, called ``Fritz''.
On each kernel, Fritz runs a number of userspace programs which test functionality ranging from the basic process lifecycle, to robustness against corner-case security vulnerabilities, to long-term stability under large stress tests.
Passing Fritz's tests constitutes 30\% of the kernel project's grade.

Unfortunately, due to the nondeterministic nature of many common bugs in student code, Fritz is unable to verify any submission's correctness with complete certainty.
(The hit-or-miss nature of Fritz's bugfinding motivated our work on Landslide.)

\subsubsection{Manual inspection}
Finally, both to make up for Fritz's incompleteness and to provide personalized human feedback, each student kernel is manually graded by a member of course staff.
The instructors and teaching assistants print out each group's submitted kernel and mark it with red ink, auditing the code for code style, architectural issues, race conditions, and preemptibility.
After the inking process, each group meets with the staff member who graded them for an hour-long ``kernel interview'', essentially a debriefing in which any final misconceptions the students might have can be rectified.
Staff discretionary points constitute 20\% of the kernel project's grade.

>>>>

The work described takes place in the context of a
Computer Science class called
15-410, Operating System Design and Implementation.
It is designed for juniors and seniors in Computer Science
and Electrical and Computer Engineering.
For CS students it is one of five courses which fulfill
the ``Software Systems'' requirement (at present, the others
are Compiler Design,
Parallel Computer Architecture and Programming,
Distributed Systems,
and Computer Networks.
The prerequisite course is 15-213,
Introduction to Computer Systems,
a course which has been adopted at other
universities in the U.S.\ and worldwide~\cite{sigcse01:CSaPP}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% XXX How do we say politely "Some M.S. students
% manage to pass it too"?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section we will discuss the course learning
objectives,
outline the programming projects,
discuss our use of Wind River Simics as the
the basic simulation/debugging environment
and our approaches to grading,
and close by mentioning current limitations in the scope
of the course material.

@@

\subsubsection{Automated tests}
We run submitted kernels in an automated testing harness. The test suite is a number of userspace programs which test functionality ranging from the basic process lifecycle, to robustness against corner-case security vulnerabilities, to long-term stability under large stress tests.
Performance on these tests constitutes 30\% of the kernel project's grade.

Of course, due to the nondeterministic nature of many common bugs in student code, these tests are unable to verify a submission's correctness with complete certainty.
(This hit-or-miss nature motivated our work on Landslide.)

\subsubsection{Manual inspection}
Finally, both to make up for the tests' incompleteness and to provide personalized human feedback, each student kernel is manually graded by a member of course staff.
The instructors and teaching assistants print out each group's submitted kernel and mark it with red ink, auditing the code for code style, architectural issues, race conditions, and preemptibility.
After the inking process, each group meets with the staff member who graded them for an hour-long ``kernel interview'', essentially a debriefing in which any final misconceptions the students might have can be rectified.
Staff discretionary points constitute 20\% of the kernel project's grade.

### 2013-01-08 edupar-13/landslide.tex
polish some text

Of course, additional decision points are necessary to expose more subtle race conditions. We provide an interface for adding new decision points to refine the state space, described in Section~\ref{sec:decision}.
In order to cope with the exponentially-sized nature of state spaces with many decision points, Landslide uses the Dynamic Partial Order Reduction (DPOR) algorithm~\cite{dpor} to identify and prune redundant thread interleavings, the specifics of which are beyond the educational scope of this work.
We also provide an interface for helping Landslide further reduce the state space by considering decision points only from certain components of the kernel, which we discuss in Section~\ref{sec:focusing}.

>>>>

Of course, additional decision points are necessary to expose more subtle race conditions. We provide an interface for adding new decision points to refine the state space, described in Section~\ref{sec:decision}.
In order to cope with the exponentially-sized nature of state spaces with many decision points, Landslide uses the Dynamic Partial Order Reduction algorithm~\cite{dpor} to identify and prune redundant thread interleavings, the specifics of which are beyond the educational scope of this work.
We also provide an interface for helping Landslide further reduce the state space by considering decision points only from certain components of the kernel, which we discuss in Section~\ref{sec:focusing}.
